Demand Forecasting of individual Probability Density Functions with Machine Learning

### 2020-07-21 LaTex/paper.tex
added example code and figures (need for refinement and other data set)

The two advantages of this method, as compared to the simpler method presented in section \ref{sec:cdf_histo}, are that an inverse quantile plot supports the qualitative evaluation of the predicted individual PDFs not only globally but (1) for different specified quantiles (potentially hinting to deviations in e.g. the tails of the distributions) and (2) in dependence of arbitrary variables of the data set (potentially hinting to deviations in e.g. specific categories of a feature). Two examples for this can be found in figures \ref{fig:invquant_mean} and \ref{fig:invquant_pg} in the next section.

@@

\subsection{Mean Estimation}

...

\begin{figure}
\begin{center}
%\includegraphics[width=8cm]{../figures/cb_mean}
\caption{\label{fig:cb_mean} 2 CB analysis plots for mean model}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
%\includegraphics[width=8cm]{../figures/mean_prediction}
\caption{\label{fig:mean_prediction} time series of mean prediction and actuals for 2 product groups}
\end{center}
\end{figure}

\subsection{Variance Estimation and PDF Predictions}

...

\begin{figure}
\begin{center}
%\includegraphics[width=8cm]{../figures/cb_var}
\caption{\label{fig:cb_var} 2 CB analysis plots for variance model}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
%\includegraphics[width=8cm]{../figures/pdf_example}
\caption{\label{fig:pdf_example} PDF example}
\end{center}
\end{figure}

@@

...

\begin{figure}
\begin{center}
%\includegraphics[width=8cm]{../figures/cdf_demand}
\caption{\label{fig:cdf_demand} CDF histogram}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
%\includegraphics[width=8cm]{../figures/invquant_mean}
\caption{\label{fig:invquant_mean} invquant profile for mean prediction on X-axis}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
%\includegraphics[width=8cm]{../figures/invquant_pg}
\caption{\label{fig:invquant_pg} invquant profile for product groups on X-axis}
\end{center}
\end{figure}

... quantitative CDF accuracy ...

>>>>

The two advantages of this method, as compared to the simpler method presented in section \ref{sec:cdf_histo}, are that an inverse quantile plot supports the qualitative evaluation of the predicted individual PDFs not only globally but (1) for different specified quantiles (potentially hinting to deviations in e.g. the tails of the distributions) and (2) in dependence of arbitrary variables of the data set (potentially hinting to deviations in e.g. specific categories of a feature). Two examples for this can be found in figures \ref{fig:invquant_mean} and \ref{fig:invquant_dayofweek} in the next section.

@@

\subsection{Mean and Variance Estimations}

\textcolor{red}{...}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{../figures/mean_prediction}
\caption{\label{fig:mean_prediction} time series of mean prediction and actuals for one item in all stores}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{../figures/cdf}
\caption{\label{fig:cdf_example} CDF example}
\end{center}
\end{figure}

@@

\textcolor{red}{...}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{../figures/cdf_truth}
\caption{\label{fig:cdf_demand} CDF histogram}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{../figures/invquant_yhat_mean}
\caption{\label{fig:invquant_mean} invquant profile for mean prediction on X-axis}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{../figures/invquant_dayofweek}
\caption{\label{fig:invquant_dayofweek} invquant profile for day of week on X-axis}
\end{center}
\end{figure}

\textcolor{red}{... quantitative CDF accuracy ...}
